SMT-Boosted Security Types for Low-Level MPC

### 2025-11-14 toplas26/examples.tex
checkpoint

\begin{fpfig}[t]{2-party gate library with Beaver Triple multiplication, circuit definition, and compositional correctness conditions.}{fig-beaver}
\footnotesize
\begin{verbatimtab}
IDEALF() { (s["x"]@1 + s["y"]@2) + (s["i"]@1 * s["j"]@2) }

RECON(x) { (m[x]@1 + m[x]@2) }

BEAVERTRIP(x) {
  m[x++"c"]@3 == r[x++"a"]@3 * r[x++"b"]@3 AND
  m[x++"a"]@1 + m[x++"a"]@2 == r[x++"a"]@3 AND
  m[x++"b"]@1 + m[x++"b"]@2 == r[x++"b"]@3 AND
  m[x++"c"]@1 + m[x++"c"]@2 == m[x++"c"]@3 
}

genshares(x:string, i1:cid, i2:cid) { m[x]@i2 := (s[x] + -r[x])@i1; m[x]@i1 := r[x]@i1 }

_open(x:string, i1:cid, i2:cid, n:string){ p[x++"n"] := m[x]@i2; m[x++"p"]@i1 := p[x++"n"] + m[x]@i1 }

open(x:string) { _open(x,1,2,"1"); _open(x,2,1,"2") }

secopen(d:string;x:string,a:string) { sum(d, x, a); open(d) }

_sum(z:string, x:string, y:string, i:cid) { m[z]@i := (m[x] + m[y])@i }

sum(z:string, x:string, y:string){ _sum(z,x,y,1); _sum(z,x,y,2) }
postcondition: ( RECON(z) == RECON(x) + RECON(y) )

_mult(z : string, y : string, i : cid) {
    m[z]@i := (m[z++"d"] * m[y] + -m[z++"e"] * m[z++"a"] + m[z++"c"])@i
}

precondition: ( BEAVERTRIP(z) )
mult(z : string, x : string, y : string) {
  secopen(z++"d", x, z++"a"); secopen(z++"e", y, z++"b"); _mult(z,y,1); _mult(z,y,2)
}
postcondition: ( RECON(z) == RECON(x) * RECON(y) )

precondition: ( BEAVERTRIP("k") ) 
main() {
    genshares("x", 1, 2); genshares("y", 2, 1); genshares("i", 1, 2); genshares("j", 2, 1);
    sum("z","x","y"); mult("k","i","j"); sum("out","z","k");
    open("out");
    out@1 = m["out"]@1; out@2 =  m["out"]@2

}
postcondition: ( out@1 == IDEALF() AND out@2 == IDEALF() )
\end{verbatimtab}
\end{fpfig}

@@

\begin{fpfig}[t]{2-party gate library with Beaver Triple multiplication extended with share type annotations.}{fig-beaver-types}
\footnotesize
\begin{verbatimtab}
genshares(x:string, i1:cid, i2:cid) {
   m[x++"s"]@i1 := (s[x] + -r[x])@i2; m[x++"s"]@i2 := r[x]@i2;
   [m[x++"s"]@i1,m[x++"s"]@i2] : shares
}

([m[x]@i1, m[x]@i2] : shares)
open(x:string) {
  _open(x,1,2,"1"); _open(x,2,1,"2");
  [p[x++"1"],p[x++"2"]] : shares;
  m[d++"p"]@2 as m[d++"p"]@1  
}

precondition: ([m[x]@i1, m[x]@i2] : shares,
	       [m[a]@i1, m[a]@i2] : shares)
secopen(d:string;x:string,a:string) {
    sum(d, x, a); open(d);
    m[d++"p"]@1 as RECON(x) + r[x++a]@3;
    <m[d++"p"]@1> : public;
    <m[d++"p"]@2> : public
}

precondition: ([m[x]@1,m[x]@2] : shares;
               [m[y]@1,m[y]@2] : shares)
sum(z:string, x:string, y:string) {
    _sum(z,x,y,1); _sum(z,x,y,2);
    [m[z]@1,m[z]@2] : shares
}
postcondition: ( RECON(z) == RECON(x) + RECON(y) )

precondition: ( [m[x]@1,m[x]@2] : shares;
                [m[y]@1,m[y]@2] : shares;
	        [m[x++"c"]@1,m[x++"c"]@2] : shares ),
	       ( BEAVERTRIP(z) )
mult(z : string, x : string, y : string) {
    secopen(z++"d", x, z++"a"); secopen(z++"e", y, z++"b"); _mult(z,y,1); _mult(z,y,2);
    [m[z]@i1,m[z]@i2] : shares
}
postcondition: ( RECON(z) == RECON(x) * RECON(y)) )
\end{verbatimtab}
\end{fpfig}

@@

\begin{fpfig}[t]{2-party gate library with Beaver Triple multiplication extended with BDOZ MACs.}{fig-beaver-bdoz}
\footnotesize
\begin{verbatimtab}
MACOK(x, i1, i2) { m[x++"m"]@i2 == m[x++"k"]@i1 + (m["delta"]@i1 * m[x++"s"]@i2) }

MACed(x) { MACOK(x, 1, 2) AND MACOK(x, 2, 1) }

_open(x:string, i1:cid, i2:cid, n:string){
    p[x++"sn"] := m[x++"s"]@i2;
    p[x++"mn"] := m[x++"m"]@i2;
    assert(p[x++"mn"] = m[x++"k"] + (m["delta"] * p[x++"sn"]))@i1;
    m[x++"p"]@i1 := p[x++"sn"] + m[x]@i1
}

precondition: ( MACed(x) )
open(x:string) { _open(x,1,2,"1"); _open(x,2,1,"2") }

_sum(z:string, x:string, y:string, i:cid){
    m[z++"s"]@i := (m[x++"s"] + m[y++"s"])@i;
    m[z++"m"]@i := (m[x++"m"] + m[y++"m"])@i;
    m[z++"k"]@i := (m[x++"k"] + m[y++"k"])@i
}

precondition: ( MACed(x) AND MACed(y) )
sum(z:string, x:string, y:string){ _sum(z,x,y,1); _sum(z,x,y,2) }
postcondition: ( MACed(z) AND RECON(z) == RECON(x) + RECON(y) )

_mult(z : string, y : string, i : cid) {
   m[z++"s"]@i := (m[z++"d"] * m[y++"s"] + -m[z++"e"] * m[z++"as"] + m[z++"cs"])@i;
   m[z++"m"]@i := (m[z++"d"] * m[y++"m"] + -m[z++"e"] * m[z++"am"] + m[z++"cm"])@i;
   m[z++"k"]@i := (m[z++"d"] * m[y++"k"] + -m[z++"e"] * m[z++"ak"] + m[z++"ck"])@i
}

precondition: ( MACed(x) AND MACed(y) AND
                MACed(z++"a") AND MACed(z++"b") AND MACed(z++"c") AND BEAVERTRIP(z) )
mult(z : string, x : string, y : string) {
    secopen(z++"d", x, z++"a"); secopen(z++"e", y, z++"b"); _mult(z,y,1); _mult(z,y,2);
}
postcondition: ( RECON(z) == RECON(x) * RECON(y) )
\end{verbatimtab}
\end{fpfig}

>>>>

\input{beaver}

@@

@@
